\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2018-08-16 sections/methods.tex
Do not include method descriptions in the supplementary section
Minor style updates
Update methods

    \vspace{-5mm}
    \begin{itemize}
      \item The mock community 16S datasets were obtained from mockrobiota \cite{Bokulich2016}. We used samples (\hl{enter id number}) for this study.
      \item The real datasets were control samples (49samples) \todo[size=\footnotesize]{Check the exact number} of a fecal microbiome transplant study obtained from \cite{Kang2017}.
      \item Simulated data was generated using Grinder \cite{Angly2012}.
    \end{itemize}

@@

    Some key features of the pipeline include modularity, flexibility and ease-of-use.
    The entire pipeline consists of modules which can be modified, reordered or replaced appropriately using a simple configuration script.
    The configuration script lists the steps to be performed during runtime, along with the parameters to be used (optional) for the various steps.
    Since the entire pipeline run-through is stored in the form of a text file (the configuration file), subsequent runs are highly reproducible and changes can be easily tracked using version control.
    The pipeline allows for automatic parallelization of all possible processes, both within and across samples.
    In addition to the Python package, the entire pipeline has been containerized into a Docker \cite{Merkel1994} image (\hl{dockerhub link}) for easy deployment and setup.
    The main components of the pipeline are detailed in the following sections.

    \todo[size=\footnotesize]{Should be in the supplementary section}
    \subsubsection*{Denoising and Clustering}
      \vspace{-5mm}
      This module deals with processing the raw 16S sequence data into \ac{otu} or \ac{esv} count tables.
      It consists of three processes:
      \begin{itemize}
        \item The quality control process handles the demultiplexing and quality control steps such as trimming adapters and trimming low-quality nucleotide stretches from the sequences.
        \item The denoise/cluster process handles the conversion of the demultiplexed, trimmed sequences into \ac{otu} or \ac{esv} count tables (some methods perform clustering and taxonomy assignment in the same step).
        \item The chimera checking process handles the removal of chimeric sequences created during the \ac{pcr} step.
      \end{itemize}
      The output of this module is a counts matrix that describes the number of reads of a particular \ac{otu} or \ac{esv} (rows of the matrix) present in each sample (columns of the matrix). The pipeline incorporates \ac{qiime1} \cite{Caporaso2010}, \ac{qiime2}, \ac{dada2} \cite{Callahan2016} and Deblur \cite{Amir2017} tools in this module.

    \subsubsection*{Taxonomy Assignment}
      \vspace{-5mm}
      This module deals with assigning taxonomies to either the representative sequences of the \ac{otu}s or directly to the \ac{esv}s.
      In order to assign taxonomies to a particular sequence we use:
      \begin{itemize}
        \item A taxonomy database, which is a collection of 16S sequences of known organisms.
        \item A query tool, which allows one to compare a sequence of interest to all the sequences in the database to find the best match.
      \end{itemize}
      The pipeline incorporates \ac{gg} \cite{DeSantis2006}, SILVA \cite{Quast2012} and the \ac{ncbi} \cite{Sayers2009} databases for taxonomy assignment

>>>>

    \vspace{-5mm}
    \begin{itemize}
      \item The mock community 16S datasets were obtained from mockrobiota \cite{Bokulich2016}. We used mock numbers (\hl{enter id number}) for this study.
      \item The real datasets were control samples (49samples) \todo[size=\footnotesize]{Check the exact number} of a fecal microbiome transplant study obtained from \cite{Kang2017}.
      \item Simulated data was generated using Grinder \cite{Angly2012}.
    \end{itemize}

    \subsubsection*{Synthetic data}

    \todo[size=\footnotesize]{Detailed options used to generate the data}

@@

    Some key features of the pipeline include modularity, flexibility and ease-of-use.
    The entire pipeline consists of modules which can be modified, reordered or replaced appropriately using a simple configuration script.
    The configuration script lists the steps to be performed during runtime, along with the parameters to be used (optional) for the various steps.
    Since the entire pipeline run-through is stored in the form of a text file (the configuration file), subsequent runs are highly reproducible and changes can be easily tracked using version control.
    The pipeline allows for automatic parallelization of all possible processes, both within and across samples.
    In addition to the Python package, the entire pipeline has been containerized into a Docker \cite{Merkel1994} image (\hl{dockerhub link}) for easy deployment and setup.

    \hl{Package usage details}

    The main components of the pipeline are detailed in the following sections.

    \subsubsection*{Denoising and Clustering}
      \vspace{-5mm}
      This module deals with processing the raw 16S sequence data into \ac{otu} or \ac{esv} count tables.
      It consists of three processes:
      \begin{itemize}
        \item The quality control process handles the demultiplexing and quality control steps such as trimming adapters and trimming low-quality nucleotide stretches from the sequences.
        \item The denoise/cluster process handles the conversion of the demultiplexed, trimmed sequences into \ac{otu} or \ac{esv} count tables (some methods perform clustering and taxonomy assignment in the same step).
        \item The chimera checking process handles the removal of chimeric sequences created during the \ac{pcr} step.
      \end{itemize}
      The output of this module is a counts matrix that describes the number of reads of a particular \ac{otu} or \ac{esv} (rows of the matrix) present in each sample (columns of the matrix).
      The pipeline incorporates \ac{qiime1} \cite{Caporaso2010}, \ac{qiime2}, \ac{dada2} \cite{Callahan2016} and Deblur \cite{Amir2017} tools in this module.

    \subsubsection*{Taxonomy Assignment}
      \vspace{-5mm}
      This module deals with assigning taxonomies to either the representative sequences of the \ac{otu}s or directly to the \ac{esv}s.
      In order to assign taxonomies to a particular sequence we use:
      \begin{itemize}
        \item A taxonomy database, which is a collection of 16S sequences of known organisms.
        \item A query tool, which allows one to compare a sequence of interest to all the sequences in the database to find the best match.
      \end{itemize}
      The pipeline incorporates \ac{gg} \cite{DeSantis2006}, SILVA \cite{Quast2012} and the \ac{ncbi}~\cite{Sayers2009} databases for taxonomy assignment
